\bf Adaption of the Chumbley Score to matching of bullet striation marks

### 2018-04-20 doc/paper.Rmd
wv 60

if (!file.exists("../data/invprofiles.rds")) {
  files <- dir("../data/inverse-profiles/", pattern="rds")
  allinv <- data.frame()
  for (file in files) {
    tmp <- readRDS(file=file.path(path="../data/inverse-profiles", file)) 
    allinv <- rbind(allinv, tmp)
  }
  allinv <- allinv %>% filter(land1_id < land2_id)
  allinv$coarse <- allinv$coarseness
  allinv <- allinv %>% select(-coarseness)
  saveRDS(allinv, file="../data/invprofiles.rds")
} else {
  allinv <- readRDS("../data/invprofiles.rds")
}

@@

Initially, the default settings suggested in \citet{hadler} were used: $w_o = 120$ pixels or about 190 $\mu m$ (ten percent of the average length of profiles) and coarseness $c = 0.25$. 
\autoref{fig:fails} shows the percentage of failed tests among the 85,491 land-to-land comparisons of the NIST data for different values of the validation window size $w_v$. For same-source lands up to 12.5 percent of the tests fail using CS1. The highest percentage of failed tests under CS2 is 0.9% for different source tests using a validation window size $w_v$ of 50 pixels. }

@@

fails %>% 
  ggplot(aes(x = wv, y = failed/n*100, colour=factor(match), shape=factor(match))) +
  geom_point(size=3) +
  xlab("Size of validation window in pixels") +
  ylab("Percent of failed tests") +
  theme_bw() +
  scale_colour_brewer("Same-source", palette="Set1") +
  scale_shape_discrete("Same-source") +
  ylim(c(0,13)) +
  facet_wrap(~method, labeller="label_method")
```

@@

```{r profile-sketch, fig.height = 5, fig.width='\\textwidth', fig.cap="Overview of the effect of different coarseness parameters $c$ on the profile shown in Figure \\ref{fig:sigs-profiles} (top). The bottom row shows histograms of  the (relative) optimal locations $t^o$ identified in the optimization step for different values of the coarseness parameter $c$. "}
profile <- sigs_graphics[[1]] %>% filter(land_id==19)
profile$lw10 <- lowess(x = profile$y, y = profile$value, f=.10)$y
profile$lw15 <- lowess(x = profile$y, y = profile$value, f=.15)$y
profile$lw20 <- lowess(x = profile$y, y = profile$value, f=.20)$y
profile$lw25 <- lowess(x = profile$y, y = profile$value, f=.25)$y
profile$lw30 <- lowess(x = profile$y, y = profile$value, f=.30)$y
#profile$lw50 <- lowess(x = profile$y, y = profile$value, f=.5)$y
#profile$lw75 <- lowess(x = profile$y, y = profile$value, f=.75)$y
#profile$lw100 <- lowess(x = profile$y, y = profile$value, f=1)$y

@@

p2 <- profc %>% 
  ggplot(aes(x = locations/(length-wo))) +
  geom_histogram(binwidth = 0.025) +
  facet_grid(.~coarseness, labeller="label_both") + 
  theme_bw() +
  xlab(expression("Relative optimal location "~t^"*")) +
  ylab("Number of profiles")

>>>>

if (!file.exists("../data/invprofiles.rds")) {
  files <- dir("../data/inverse-profiles/", pattern="rds")
  allinv <- data.frame()
  for (file in files) {
    tmp <- readRDS(file=file.path(path="../data/inverse-profiles", file)) 
    allinv <- rbind(allinv, tmp)
  }
  allinv <- allinv %>% filter(land1_id < land2_id)
  allinv <- allinv %>% select(-coarseness)
  saveRDS(allinv, file="../data/invprofiles.rds")
} else {
  allinv <- readRDS("../data/invprofiles.rds")
}

@@

Initially, the default settings suggested in \citet{hadler} were used: $w_o = 120$ pixels or about 190 $\mu m$ (ten percent of the average length of profiles) and coarseness $c = 0.25$. 
\autoref{fig:fails} shows the percentage of failed tests among the 85,491 land-to-land comparisons of the NIST data for different values of the validation window size $w_v$. For same-source lands up to 12.5 percent of the tests fail using CS1. The highest percentage of failed tests under CS2 is 1.3% for different source tests using a validation window size $w_v$ of 60 pixels.

@@

fails %>% 
  ggplot(aes(x = wv, y = failed/n*100, colour=factor(match), shape=factor(match))) +
  geom_point(size=3) +
  xlab("Size of validation window in pixels") +
  ylab("Percent of failed tests") +
  theme_bw() +
  scale_colour_brewer("Same-source", palette="Set1") +
  scale_shape_discrete("Same-source") +
  ylim(c(0,13)) +
  facet_wrap(~method, labeller="label_both")
```

@@

```{r profile-sketch, fig.height = 4.5, fig.width='\\textwidth', fig.cap="Overview of the effect of different coarseness parameters $c$ on the profile shown in Figure \\ref{fig:sigs-profiles} (top). The bottom row shows histograms of  the (relative) optimal locations $t^o$ identified in the optimization step for different values of the coarseness parameter $c$. "}
profile <- sigs_graphics[[1]] %>% filter(land_id==19)
profile$lw10 <- lowess(x = profile$y, y = profile$value, f=.10)$y
profile$lw15 <- lowess(x = profile$y, y = profile$value, f=.15)$y
profile$lw20 <- lowess(x = profile$y, y = profile$value, f=.20)$y
profile$lw25 <- lowess(x = profile$y, y = profile$value, f=.25)$y
profile$lw30 <- lowess(x = profile$y, y = profile$value, f=.30)$y
#profile$lw50 <- lowess(x = profile$y, y = profile$value, f=.5)$y
#profile$lw75 <- lowess(x = profile$y, y = profile$value, f=.75)$y
#profile$lw100 <- lowess(x = profile$y, y = profile$value, f=1)$y

@@

p2 <- profc %>% 
  ggplot(aes(x = locations/(length-wo))) +
  geom_histogram(binwidth = 0.01) +
  facet_grid(.~coarseness, labeller="label_both") + 
  theme_bw() +
  xlab(expression("Relative optimal location "~t^"*")) +
  ylab("Number of profiles")

### 2018-04-20 doc/paper.tex
wv 60

Initially, the default settings suggested in \citet{hadler} were used:
\(w_o = 120\) pixels or about 190 \(\mu m\) (ten percent of the average
length of profiles) and coarseness \(c = 0.25\). \autoref{fig:fails}
shows the percentage of failed tests among the 85,491 land-to-land
comparisons of the NIST data for different values of the validation
window size \(w_v\). For same-source lands up to 12.5 percent of the
tests fail using CS1.
\hh{XXX Currently running CS2 for these settings for a comparison.}

@@

\caption{Percent of failed land-to-land comparisons using an optimization window $w_o = 120$ and a coarseness of $c = 0.25$. With an increase in the size of the validation window  a higher percentage of tests fails. The percentage of failures is higher for same-source lands than for different source lands.}\label{fig:fails}
\end{figure}

\hh{XXX Conclusion: the number of failed tests goes down - a lot. XXX}

>>>>

Initially, the default settings suggested in \citet{hadler} were used:
\(w_o = 120\) pixels or about 190 \(\mu m\) (ten percent of the average
length of profiles) and coarseness \(c = 0.25\). \autoref{fig:fails}
shows the percentage of failed tests among the 85,491 land-to-land
comparisons of the NIST data for different values of the validation
window size \(w_v\). For same-source lands up to 12.5 percent of the
tests fail using CS1. The highest percentage of failed tests under CS2
is 0.9\% for different source tests using a validation window size
\(w_v\) of 50 pixels.

@@

\caption{Percent of failed land-to-land comparisons using an optimization window $w_o = 120$ and a coarseness of $c = 0.25$. With an increase in the size of the validation window  a higher percentage of tests fails under both methods (CS1) and (CS2), but the percentage of failed tests is much smaller under (CS2).}\label{fig:fails}
\end{figure}
